Seagrass mapping and monitoring \\ along the coasts of Crete, Greece

### 2011-02-14 MScDiplom_Lemenkova.tex
Comment 22 of Valentijn: Fig.4.5: added MERIS spectral bands as stripes

\begin{figure}[H]
	\centering
	\subfloat [depth of 0.5 m]{\label{fig:32a}\includegraphics[width=0.4\textwidth]{Fig-32a.jpg}}
	\subfloat [depth of 2.0 m]{\label{fig:32b}\includegraphics[width=0.4\textwidth]{Fig-32b.jpg}}\\
	\subfloat [depth of 3.5 m]{\label{fig:32c}\includegraphics[width=0.4\textwidth]{Fig-32c.jpg}}
	\subfloat [depths of 0.5, 2.0 and 3.5 m]{\label{fig:32d}\includegraphics[width=0.4\textwidth]{Fig-32d.jpg}}
	\caption{Remote sensing reflectance of \textit{P.oceanica} at various depths, simulated for broadband sensors. Pages: $<$\pageref{page-37}$>$, $<$\pageref{page-32}$>$}
	\label{fig:4.9}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\subfloat [depth of 0.5 m]{\label{fig:32a}\includegraphics[width=0.4\textwidth]{Fig-32a-SB.jpg}}
	\subfloat [depth of 2.0 m]{\label{fig:32b}\includegraphics[width=0.4\textwidth]{Fig-32b-SB.jpg}}\\
	\subfloat [depth of 3.5 m]{\label{fig:32c}\includegraphics[width=0.4\textwidth]{Fig-32c-SB.jpg}}
	\subfloat [depths of 0.5, 2.0 and 3.5 m]{\label{fig:32d}\includegraphics[width=0.4\textwidth]{Fig-32d-SB.jpg}}
	\caption{Simulated remote sensing reflectance of \textit{P.oceanica} at various depths. Pages: $<$\pageref{page-37}$>$, $<$\pageref{page-32}$>$.\\ Vertical stripes show coverage of spectral bands by MERIS sensor}
	\label{fig:4.9}
\end{figure}
